---
title: "Detection probability"
author: "Joe Roe"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Detection probability}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography: ../inst/REFERENCES.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

First, let's load `fieldwalkr` and generate some some dummy data to simulate a survey.

```{r, fig.show='hold'}
library("fieldwalkr")
library("sf")
library("ggplot2")

frame <- rpolygon()                   # Sample frame
sites <- st_sample(frame, 100)        # Target points
units <- quadrats(frame, size = 200)  # Survey units

# Plot
theme_nocoords <- function() {
  return(theme(axis.text = element_blank()))
}

ggplot() + 
  geom_sf(data = frame, fill = "white") +
  geom_sf(data = sites) +
  ggtitle("sites") +
  theme_nocoords()

ggplot() + 
  geom_sf(data = frame, fill = "white") + 
  geom_sf(data = units, fill = NA) +
  ggtitle("units") +
  theme_nocoords()
```

## Detection functions

Modelling detection probability in `fieldwalkr` employs the concept of a *detection functions*.
This concept is drawn from search theory, and specifically Banning and colleague's application of search theory to archaeological survey [@Banning2002-uv; @Banning2006-js; @Banning2011-wo].

### 

### Custom detection functions

## References
